---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "figs/README-"
)
```

Ever wonder what Bill Murray might look like if he were the same colors as a bowl of celery?

Perhaps you've been curious about how that bowl of celery might look if it was, say, the color of the American flag... 

What if I told you these daily quandaries had been solved?

**Search no more, for here lay your answers! Read on to discover the answers to these, and more!**

#RImagePalette: Extract colors from an image, and use it in plots or for fun!

The `RImagePalette` package lets you use the colors from an image you like to create pretty plots. 

This package is available from [CRAN](https://cran.r-project.org/web/packages/RImagePalette/index.html) using:

```{r,eval=FALSE}
install.packages("RImagePalette")
library(RImagePalette)
```
```{r,echo=FALSE, message=FALSE}
devtools::load_all(".")
```



#Just for fun



You didn't think I forgot about old Bill and celery plate complexion, did you?

```{r}
celery <- jpeg::readJPEG("figs/Lunch.jpg")
billMurray <- jpeg::readJPEG("figs/LifeAquatic.jpg")
set.seed(10)
switch_colors(billMurray, celery, source_colors = 5, choice=median)

```

```{r}
america <- jpeg::readJPEG("figs/AmericanFlag.jpg")
obama <- jpeg::readJPEG("figs/Obama.jpg")
switch_colors(obama, america, source_colors=5, smoothness=500)
```



#Inspiration:

https://github.com/lokesh/color-thief/blob/master/src/color-thief.js

https://github.com/karthik/wesanderson

http://www.r-bloggers.com/towards-yet-another-r-colour-palette-generator-step-one-quentin-tarantino/

